TE_computation

### 2021-03-22 computational model/TE_computation_Simulation.Rmd
changing I to IND

# Simulation3: TE = I * (D*N/V)
## Defining the independence parameter I
I1 = 1.5 # I > 1, TEs are MORE easily learned than unique words
I2 = 0.5 # I < 1, TEs are LESS easily learned than unique words

## Visualizing the simulation
Simulation3 <- data_Simulation3 %>%
  ## Calculate where I > 1
  mutate(TE_easier = I1*(D*N/V)) %>%
  ## Calculate where I < 1
  mutate(TE_harder = I2*(D*N/V)) %>%
  # Round to keep whole numbers only
  mutate_at(vars(-B), round, 0) %>%
  # Prepare dataset to plot
  pivot_longer(c(TE, TE_harder, TE_easier), 
               names_to = "Model", values_to = "number_TE") %>%
  mutate(Model = factor(Model, levels=c("TE_harder", "TE", "TE_easier"))) %>%
  mutate(Model = recode(Model, 
                        TE = "I = 1 (assuming independence of D and N)",
                        TE_easier = "I = 1.5 (TEs are more easily learned)",
                        TE_harder = "I = 0.5 (TE are less easily learned)")) %>%
  mutate(bin_B = cut(B, breaks = 6, 
                     labels = c("0.5", "0.6", "0.7", "0.8", "0.9", "1"))) %>%
  # ggplot
  ggplot(aes(x = W, y = number_TE, color = bin_B)) +
  stat_smooth(method = lm, se = F) +
  theme_minimal() + 
  facet_grid(. ~ Model) +
  ylim(0, 600) +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "bottom") +
  theme(plot.title = element_text(hjust = 0.5),
        text = element_text(size=12),
        panel.spacing.x = unit(2, "lines"),
        panel.background = element_rect(fill = NA, color = "black")) +
  labs(x = "Total word vocabulary (W)", 
       y = "Total number of translation equivalents (TE)", 
       color = "Balance (B)") +
  guides(colour = guide_legend(nrow = 1))

>>>>

# Simulation3: TE = IND * (D*N/V)
## Defining the independence parameter I
IND1 = 1.5 # IND > 1, TEs are MORE easily learned than unique words
IND2 = 0.5 # IND < 1, TEs are LESS easily learned than unique words

## Visualizing the simulation
Simulation3 <- data_Simulation3 %>%
  ## Calculate where IND > 1
  mutate(TE_easier = IND1*(D*N/V)) %>%
  ## Calculate where IND < 1
  mutate(TE_harder = IND2*(D*N/V)) %>%
  # Round to keep whole numbers only
  mutate_at(vars(-B), round, 0) %>%
  # Prepare dataset to plot
  pivot_longer(c(TE, TE_harder, TE_easier), 
               names_to = "Model", values_to = "number_TE") %>%
  mutate(Model = factor(Model, levels=c("TE_harder", "TE", "TE_easier"))) %>%
  mutate(Model = recode(Model, 
                        TE = "IND = 1 (assuming independence of D and N)",
                        TE_easier = "IND = 1.5 (TEs are more easily learned)",
                        TE_harder = "IND = 0.5 (TE are less easily learned)")) %>%
  mutate(bin_B = cut(B, breaks = 6, 
                     labels = c("0.5", "0.6", "0.7", "0.8", "0.9", "1"))) %>%
  # ggplot
  ggplot(aes(x = W, y = number_TE, color = bin_B)) +
  stat_smooth(method = lm, se = F) +
  theme_minimal() + 
  facet_grid(. ~ Model) +
  ylim(0, 600) +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "bottom") +
  theme(plot.title = element_text(hjust = 0.5),
        text = element_text(size=12),
        panel.spacing.x = unit(2, "lines"),
        panel.background = element_rect(fill = NA, color = "black")) +
  labs(x = "Total word vocabulary (W)", 
       y = "Total number of translation equivalents (TE)", 
       color = "Balance (B)") +
  guides(colour = guide_legend(nrow = 1))
